\chapter{Acknowledgments}

First and foremost, I would like to thank my parents for always pushing me.  I would not have achieved anything close to a PhD without them.  To my mother, for making me call her and discuss my day, even when I wanted to.  You always made me laugh and picked me up when I questioned continuing. Your life lessons and advice have been invaluable. To my father, you are the most hard-working person I have ever met and hope to even become $\frac{1}{10}$ as much as you are.  When you paid me to study for my AP tests instead of stressing about working at a crappy job stayed with me to make the right things a priority.  A thank you to my sisters, who pushed me in different ways, but with equal effectiveness.  Your support can never be measured.  I love you all deeply. 

I would like to thank Stephanie Michele Zamora for helping me in every way, including with this thesis.  Without your love and support, I would not be here and cannot ask for a better partner.

Andrew Jaffe, thank you for our many consultations and discussions, mostly over beers.

A crucial and special thank you to my friend and college Elizabeth Margaret Sweeney (my ``work wife''), with whom I have gone over all projects in excruciating detail.  I have found your comments to be invaluable and with you I have had the important discussions during many projects.  Thank you for telling me to keep writing, at times to take my own advice, and hundreds of lunches (including work lunches) that made going into the office worthwhile.  I will never find a similar colleague and friend, one forged through the depths of probability theory, bounded in work in neuroimaging, and solidified with our statistical lineage and shared moments throughout our work.  It is much easier to leave Hopkins knowing you are moving on as well.

I would like to thank the Department of Biostatistics and the Epidemiology and Biostatistics training grant from the NIH (T32AG021334), which gave me the required support to work on projects I felt relevant.  Thank you to Dr. Michelle Carlson and Dr. Ravi Varadhan for your mentorship.  

Thank you Dr. Taki Shinohara for the collaboration and discussion.  You have always given thoughtful and criticism and advice. and I wish you the best in your career. 

Thank you Dr. Daniel Hanley for all the close collaborations over the years.  The topics of the thesis are a testament to how closely I have worked with you and your team.  I have always valued your frank criticism and your challenge to remember the clinical implications of my work.   

Thank you Dr. Brian Caffo for encouraging me to come back to the PhD program after advising me in my Master's degree. It has been the best and most transformative decisions of my life. I will always remember you having time to chat, whether about statistics, the department, or general fun tech stuff.  

Thank you Dr. Ciprian Crainiceanu for all your advising, about my degree, job search, and life.  Your help on all my projects has been crucial.  Your help on the stuff ``not in the curriculum'', in some ways, has been even more useful .  You taught me how to create a large network of connections, reminded me that of the many things important outside school, and have been a strong advocate for me in every way.   You have shown the dedication of a true advisor. 

